Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-04 paper.tex

While many design methods envolved with new memory technologies endeavor to
reduce the memory access latency of going off-chip, this work employs the hybrid
on-chip memory and reconfiguration to minimize off-chip bandwidth requirement.
For each level of memory, we select the memory technology that has the highest
provided bandwidth within given capacity. On top of such hardware hierarchy
design, we apply dynamic memory system reconfiguration that awares of the
bandwidth demand of a specific set of applications.

Based on our memory technology exploration, we now provide an overview of our
bandwidth-aware architecture (Section~\ref{sec:hierarchy}) , and then discuss the details on the hardware
support (Section 3.2) and OS support (Section 3.3) required for achieving high
performance on this architecture.

>>>>

Based on our memory technology exploration, we now provide an overview of BROM
design. While many design methods envolved with new memory technologies endeavor
to reduce the off-chip memory access latency, this work focuses on minimize
off-chip bandwidth requirement by employing hybrid on-chip memory and
reconfiguration. For each level of memory, we select the memory technology that
has the highest provided bandwidth within given capacity. On top of such
hardware hierarchy design, we apply dynamic memory system reconfiguration with
the bandwidth demand of a specific set of applications as the major metric. One
desirable characteristic of BROM is that it provides prioritized access to the
residual memory capacity available at runtime instead of sharing it among all
data flows. By having control over the residual capacity, we can better utilize
the limited resources to enhance system performance. The hardware
reconfiguration is further facilitated by software prediction engine. Rather
than conventional last value predictors and table-based predictors, we employ a
probablity-based predictor that can achieve higher accuracy with small
performance overhead.
